О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-27 pps-linear-bound/pps-linear-lower-bound.tex
Proofreading by Usachev - p. 11

	If (a) is true for both points, then $M\subset l$ and thus $M$ is not an integral point set.
	If (a) is true for one point and (b) is true for another, then the claim of the lemma follows.
	So, suppose the contrary, i.e. both points $M_3$ and $M_4$ belong to $m$.

	The area of the triangle $M_1 M_3 M_4$ is rational because $|M_3 - M_4| \in \mathbb{Z}$.
	Thus, the characteristic of $M$ is 1,
	and there is a Cartesian coordinate system such that $M_1=(-1/2,0)$, $M_2=(1/2,0)$, $M_3=(0, a/2)$
	(see~\cite[Theorem 4]{our-vmmsh-2018}).
	It is clear that $a\neq 0$.
	We set $b = |M_1 - M_3|$ and $O=(0,0)$.
	Applying the Pythagorean theorem to triangle $OM_1M_3$, we obtain the following Diophantine equation:
	\begin{equation}
		\frac{1}{4} + \frac{a^2}{4} = b^2
		,
	\end{equation}
	or, which is the same,
	\begin{equation}
		1 + a^2 = (2b)^2
		,
	\end{equation}
	that has no integral solutions.
	This contradiction concludes the proof.
\end{proof}

@@

\begin{theorem}
	\label{thm:minimeter_1_planar}
	For every $n\geq 3$ there is a planar intergal set $M$ of $n$ points
	such that for some $M_1,M_2 \in M$ equality $|M_1 M_2|=1$ holds.
	This set consists of $n-1$ points, including $M_1$ and $M_2$, on a straight line and one point out of the line.

>>>>

	If (a) is true for both points, then $M\subset l$ and thus $M$ is not an integral point set.
	If (a) is true for one point and (b) is true for another, then the claim of the lemma follows.
	So, suppose to the contrary, that both points $M_3$ and $M_4$ belong to $m$.

	The area of the triangle $M_1 M_3 M_4$ is rational because $|M_3 - M_4| \in \mathbb{Z}$.
	Thus, the characteristic of $M$ is 1,
	and there is a Cartesian coordinate system such that $M_1=(-1/2,0)$, $M_2=(1/2,0)$, $M_3=(0, a/2)$
	(see~\cite[Theorem 4]{our-vmmsh-2018}).
	It is clear that $a\neq 0$.
	We set $b = |M_1 - M_3|$ and $O=(0,0)$.
	Applying the Pythagorean theorem to triangle $OM_1M_3$, we obtain the following Diophantine equation:
	\begin{equation}
		\frac{1}{4} + \frac{a^2}{4} = b^2
		,
	\end{equation}
	or, equivalently,
	\begin{equation}
		1 + a^2 = (2b)^2
		.
	\end{equation}
	This equation has no integral solutions.
	This contradiction concludes the proof.
\end{proof}

@@

\begin{theorem}
	\label{thm:minimeter_1_planar}
	For every $n\geq 3$ there is a planar integral set $M$ of $n$ points
	such that for some $M_1,M_2 \in M$ equality $|M_1 M_2|=1$ holds.
	This set consists of $n-1$ points, including $M_1$ and $M_2$, on a straight line and one point out of the line.
